## Risk Models for AKI, ARF and RRT in CHF

========================================================




```{r CHF AKI RIFLE1, cache=FALSE}


chf <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/chf.csv")


```

## Development of RIFLE grade 1 AKI in Hospitalised CHF Patients.

```{r CHF AKI RIFLE 1 GLM, cache=FALSE, warning=FALSE}



chf.aki1<- glm(devaki~log(PROCALCITONIN.d01)+LACTATE.d01+WBC.d01+Htn+DM2+PHtn+min_sodium+CR.d01+gender+ALB.d01+AGE+BUN.Cr+HCO3,data=chf, family=binomial(link=logit))

summary(chf.aki1)

int <- exp(confint(chf.aki1))
odds <- exp(coef(chf.aki1))
aki1oddstable <- cbind(odds,int)
aki1oddstable
stargazer(aki1oddstable)
```

## Model for Development of RIFLE 3  AKF in Hospitalised CHF Patients.

Criterion for RIFLE 3 AKF as follows:

devakirifle3=(d2max_cr/CR.d01)>=3)
rifle4 = (CR.d01 >=4 & ((d2max_cr-CR.d01)>=0.5)))
rifle3 = (devakirifle3=="TRUE" | rrtbin =="TRUE" | rifle4 == "TRUE"))


```{r, cache=FALSE, warning=FALSE}
## glm for rifle3
chfrifle3 <- glm(rifle3~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+PHtn+Htn+AGE+min_sodium+min_hb+BUN.Cr+HCO3,data=chf, family=binomial(link=logit))

summary(chfrifle3)


##odds ratio table
int <- exp(confint(chfrifle3))
odds <- exp(coef(chfrifle3))
akioddstable <- cbind(odds,int)
akioddstable


```

## Model for Development of RIFLE 2  AKF in Hospitalised CHF Patients.

(d2maxcr/Cr.d01 >2)

*Here we subset the anonMASTER file and define the outcome of RIFLE 2 renal injury. We subset the data for CHF patients and generate and odds ratio table.*

```{r, warning=FALSE}

chfrifle2 <- glm(devakirifle2~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+AGE+PHtn+Htn+ESLD+BUN.Cr+HCO3,data=chf, family=binomial(link=logit))
summary(chfrifle2)


int <- exp(confint(chfrifle2))
odds <- exp(coef(chfrifle2))
akioddstable <- cbind(odds,int)
akioddstable

```
