## Risk Models for AKI, ARF and RRT in CHF models

========================================================



```{r ,cache=TRUE,echo=TRUE }
opts_chunk$set(WARNING=FALSE, echo=FALSE)
```


```{r}

```


```{r CHF AKI RIFLE1, cache=TRUE}


chf <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/chf.csv")
chf$X.1 <- NULL
library(xtable)
library(vcd)
mytable <- xtabs(~Htn+PHtn+ESLD, data=chf)
ftable(mytable)

```

## Development of RIFLE grade 1 AKI in Hospitalised CHF Patients.

```{r CHF AKI RIFLE 1 GLM,, cache=FALSE, warning=FALSE}



chf.aki<- glm(devaki~log(PROCALCITONIN.d01)+LACTATE.d01+WBC.d01+DM2+PHtn+min_sodium+CR.d01+gender+ALB.d01+AGE,data=chf, family=binomial(link=logit))

summary(chf.aki)

int <- exp(confint(chf.aki))
odds <- exp(coef(chf.aki))
akioddstable <- cbind(odds,int)
akioddstable
akioddstable<- xtable(akioddstable)
```

## Model for Development of RIFLE 3 Hospitaled AKF in CHF Patients.

Criterion for RIFLE 3 AKF as follows:

devakirifle3=(d2max_cr/CR.d01)>=3)
rifle4 = (CR.d01 >=4 & ((d2max_cr-CR.d01)>=0.5)))
rifle3 = (devakirifle3=="TRUE" | rrtbin =="TRUE" | rifle4 == "TRUE"))


```{r, cache=TRUE, warning=FALSE}
## glm for rifle3
chfrifle3 <- glm(rifle3~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+PHtn+Htn+AGE+min_sodium+min_hb,data=chf, family=binomial(link=logit))

summary(chfrifle3)


##odds ratio table
int <- exp(confint(chfrifle3))
odds <- exp(coef(chfrifle3))
akioddstable <- cbind(odds,int)
akioddstable


```

## Model for Development of RIFLE 2  AKF in Hospitalised CHF Patients.

(d2maxcr/Cr.d01 >2)

*Here we subset the anonMASTER file and define the outcome of RIFLE 2 renal injury. We subset the data for CHF patients and generate and odds ratio table.*

```{r, warning=FALSE}

chfrifle2 <- glm(devakirifle2~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+AGE+PHtn+Htn,data=chf, family=binomial(link=logit))
summary(chfrifle2)


int <- exp(confint(chfrifle2))
odds <- exp(coef(chfrifle2))
akioddstable <- cbind(odds,int)
akioddstable

```

