Model selection and evaluation for models that predict Acute Kidney Failure (RIFLE3) and their ROC curves.
========================================================

In this document we are selecting glm models for predicting the development of Acute Kidney Injury (specifically RIFLE 3 class) in patients with Congestive Heart Failure who are admitted to the hospital. We will be using the glmulti, pROC and other packages. We will start off by inputing a large model with many variables in our dataset.

We will generate a glm object called chfrifle3. 

```{r , cache=TRUE, eval=TRUE}

chf <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/chf.csv")
library(glmulti)
chfrifle3 <- glm(rifle3~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+PHtn+Htn+AGE+min_sodium+min_hb+BUN.Cr+HCO3,data=chf, family=binomial(link=logit))

```

## Selecting the best glm model 

that takes a bit to run. I have run it before and basically it runs through greater than 16000 models and selects the best model based on a criterion called AICc. Change eval=TRUE to run again.


```{r,cache=TRUE, echo=FALSE,eval=FALSE}
multi.chf <- glmulti(chfrifle3, # use the model with built as a starting point
                      level = 1,  #  just look at main effects
                      crit="aicc") # use AICc because it works better than AIC for small sample sizes)

summary(multi.chf)
```
Look at the top 10 models, ranked by AICc

Tada.....Best model: rifle3~1+PHtn+log(PROCALCITONIN.d01)+CR.d01+min_sodium

Here is the weightable for the top 10 models. To look at the top 10 models, ranked by AICc, turn eval=TRUE

```{r,cache=TRUE,eval=FALSE}
weightable(multi.chf)

```

## Prepare for the ROC analysis on the models

Subset out the relevant variables into a smaller dataset called chf2. And create a model object called "fit", which represents model. I treid the top model, however the AUC was in the 80s for Rifle3 and I found that by adding other variables the AUC could be improved on significantly.

# AUC for RIFLE 3 
```{r}





fit<- glm(rifle3 ~AGE+ log(PROCALCITONIN.d01)+CR.d01+PHtn+min_sodium+IHD+AFIB+CHFTYPE,data=chf, na.action=na.exclude, family=binomial(link=logit))
summary(fit)

## I added the terms LACTATE.d01 ,CHFTYPE,AFIB,AGE,IHD to get the best model based on the AUC curve.

## Load the pROC library 

library(pROC)



## Make your reciever-operater curve for RIFLE3 Injury

m.roc <- roc(chf$rifle3, predict(fit, backtransform = TRUE))
plot(m.roc)


```


# AUC for >RIFLE2 


```{r}
fit<- glm(devakirifle2 ~AGE+ log(PROCALCITONIN.d01)+CR.d01+PHtn+min_sodium+IHD+AFIB+CHFTYPE+LACTATE.d01,data=chf, na.action=na.exclude, family=binomial(link=logit))
summary(fit)

summary(fit)
## NONE OF THE ESLD PATIENTS DEVELOPED AKI2 SEE BELOW REMOVED
with(chf,table(ESLD,devakirifle2))
## I added the terms LACTATE.d01 ,CHFTYPE,AFIB,AGE,IHD to get the best model based on the AUC curve.
## Severe Imbalance in the devakirifle2 in COPD removed term.(although not sure it should be removed)
with(chf,table(COPD,devakirifle2))


m.roc <- roc(chf$devakirifle2, predict(fit, backtransform = TRUE))
plot(m.roc)


```

# AKI for >RIFLE1


```{r}
fit<- glm(devaki~ AGE+log(PROCALCITONIN.d01)+ CR.d01+PHtn+min_sodium+CHFTYPE+AFIB+ESLD+IHD+COPD+LACTATE.d01,data=chf, na.action=na.exclude, family=binomial(link=logit))
summary(fit)

m.roc <- roc(chf$devaki, predict(fit, backtransform = TRUE))
plot(m.roc)

```


## ROC curves for RIFLE 3 outcome.

RIFLE 3 AKI with day Creatinine in the model
```{r RIFLE 3 AKF with Creatinine}



set.seed(2014)
data<- chf
library(caret)
trainingRows <- createDataPartition(data$rifle3,p=0.8, list=FALSE)
training <- data[trainingRows,]
testing <- data[-trainingRows,]
train.fit<- glm(rifle3 ~ AGE + log(PROCALCITONIN.d01)+CR.d01+PHtn+min_sodium,data=training, na.action=na.exclude, family=binomial(link=logit))


library(Deducer)
rocplot(train.fit)
prediction <- predict(train.fit, backtransform=TRUE,newdata=testing)
testing.roc <- roc(testing$rifle3, prediction)
plot(testing.roc)

```


## No creatinine model; Model for prediciting RIFLE 3 ARF without usingday01 Creatinine

##Lets see if we can take day one Creatinine out of the equation and predict RIFLE 3 AKF

```{r rifle 3 modelled without day01 creatinine }
set.seed(606)
library(caret)
trainingRows <- createDataPartition(chf$rifle3,p=0.75, list=FALSE)

training <- chf[trainingRows,]
testing <- chf[-trainingRows,]

training.fit2 <- glm(rifle3 ~AGE+ log(PROCALCITONIN.d01)+PHtn+min_sodium+IHD+AFIB+CHFTYPE+COPD+Transplant.y+ALB.d01+min_hb+HCO3+ESLD:PLATELETS.d01,data=training, na.action=na.exclude, family=binomial(link=logit))
rocplot(training.fit2)

testing.fit2 <- glm(rifle3 ~AGE+ log(PROCALCITONIN.d01)+PHtn+min_sodium+IHD+AFIB+CHFTYPE+COPD+Transplant.y+ALB.d01+min_hb+HCO3+ESLD:PLATELETS.d01+ESLD:PLATELETS.d01,data=testing, na.action=na.exclude, family=binomial(link=logit))

rocplot(testing.fit2)
```

#RIFLE 2 renal injury model AUCs
___________________________________________
Lets start by partioning our data.
```{r data partioning training and testing datasets with ROC curves,eval=FALSE,echo=FALSE }

library(dplyr)
chf3 <- mutate(chf,akiR2= (devakirifle2=="TRUE" | rifle3=="TRUE"))
set.seed(44)
library(caret)
trainingRows <- createDataPartition(chf3$akiR2,p=0.7, list=FALSE)
training <- chf3[trainingRows,]
testing <- chf3[-trainingRows,]

fit<- glm(akiR2 ~AGE+ log(PROCALCITONIN.d01)+CR.d01+min_sodium+PHtn,data=training, na.action=na.exclude, family=binomial(link=logit))
summary(fit)

## I added the terms LACTATE.d01 ,CHFTYPE,AFIB,AGE,IHD to get the best model based on the AUC curve.

## Load the pROC library 

library(pROC)



## Make your reciever-operater curve for RIFLE3 Injury

training.roc <- roc(training$akiR2, predict(fit, backtransform = TRUE))
plot(training.roc)

test.roc <- roc(testing$akiR2,predict(fit,newdata=testing, backtransform=TRUE, type="response"))
plot(test.roc)



```















## Using the train function, generate models

```{r,eval=FALSE,echo=FALSE}
set.seed(1)
```

 But we should be able to preprocess with dummy vars

```{r, eval=FALSE,echo=FALSE}
dummies <- dummyVars(rifle3 ~ ., data = training)
dumb.training <-predict(dummies, newdata=training)
rifle3 <- training$rifle3
dumb.training2 <- cbind(rifle3,dumb.training)

View(dumb.training)

fit <- train(as.factor(rifle3) ~ ., data=dumb.training2, method="glm", preProcess=c("knnImpute", "center","scale"))

```


summary(fit)
## I added the terms LACTATE.d01 ,CHFTYPE,AFIB,AGE,IHD to get the best model based on the AUC curve.
## Load the pROC library
library(pROC)
## Make your reciever-operater curve for RIFLE3 Injury
training.roc <- roc(training$rifle3, predict(fit, backtransform = TRUE))
plot(training.roc)
test.roc <- roc(testing$rifle3,predict(fit,newdata=testing, backtransform=TRUE))
plot(test.roc)




```
```{r create the dummyVar test object and apply it to the test set,echo=FALSE,eval=FALSE}
rifle3 <- testing$rifle3
dummies.test <- dummyVars(rifle3~ ., data = testing)
dumb.testing <-predict(dummies.test, newdata=testing)
dumb.testing2 <- cbind(rifle3,dumb.testing)

prediction <- predict(fit,newdata=dumb.testing2)

```


