## Survival Analysis from d01 Procalcitonin Project

========================================================

```{r loading up the packages, cache=TRUE}
anonMASTER <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/anonMASTER.csv")
View(anonMASTER)
library(ggplot2)
library(caret)
library(dplyr)

```



```{r survival lactate, cache=TRUE}
data <- anonMASTER
data <- tbl_df(data)
qplot(LACTATE.d01,Survival,data=data, colour=Survival)


```

```{r, cache=TRUE}
qplot(LACTATE.d01,Survival,data=data, colour=Survival, geom=c("point","smooth"), method=lm)

```

```{r, cache=TRUE}
qplot(LACTATE.d01,Survival,data=data, colour=Transplant.y, geom=c("point","smooth"), method=lm)

```{r , cache=TRUE}
qplot(LACTATE.d01,Survival,data=data, colour=ESLD, geom=c("point","smooth"), method=lm)
```

```{r, cache=TRUE}
qplot(log(PROCALCITONIN.d01),Survival,data=data,colour=PROCALCITONIN.d01, geom=c("point","smooth"), method=lm)
```

```{r, cache=TRUE}
qplot(log(PROCALCITONIN.d01),Survival,data=data,colour=Transplant.y, geom=c("point","smooth"), method=lm)

```

```{r, cache=TRUE}
qplot(log(PROCALCITONIN.d01),Survival,data=data,colour=ESLD, geom=c("point","smooth"), method=lm)
```

```{r, cache=TRUE}
qplot(log(LACTATE.d01),Survival,data=data,colour=aki, geom=c("point","smooth"), method=lm)

```

```{r, cache=TRUE}

qplot(log(LACTATE.d01),Survival,data=data,colour=ESLD, geom=c("point","smooth"), method=lm)

```



```
