## Survival Package to look at the CHF subset in the Procalcitonin Database )(d01)

========================================================
#Here we read the chfnoesrd file into the current knitr document create a survival object and and plot a curve on it using the CHF patient in the d01 Procalcitonin dataset that do not have the ESRD.CKD5 code

```{r read chf no esrd file in , cache=TRUE}
chfnoesrd <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/chfnoesrd")
data=chfnoesrd
library(survival)
chf.surv <- with(data, Surv(time=Survival,event=event))
fit <- survfit(chf.surv ~ 1, data=data)
plot(fit)


```

We generate survival curves on CHF patients based on their Procalcitonin levels ( >2 or not.)

```{r 30 day mortality in CHF patients, cache=TRUE}
library(dplyr)
chfnoesrd2 <- mutate(chfnoesrd, ProcalGreater2 = PROCALCITONIN.d01 >=2)
data=chfnoesrd2
attach(data)
predict <- cbind(PROCALCITONIN.d01,CR.d01,VentCPT,RRTCPT,ALB.d01,WBC.d01,gender)
## create a surv object
chf.surv <- with(data, Surv(time=as.numeric(Survival),event=event))
## fit a surv object based on d01 ProcalGreater than 2
fit <- survfit(chf.surv ~ ProcalGreater2, data=data, conf.int=TRUE)
## plot KM curve with intervals
plot(fit, col=c("green","purple") ,conf.int=TRUE)
## Test for differences in survival objects using survdiff ()
diff <- with(data, survdiff(Surv(time=Survival,event=event)~ProcalGreater2),rho=1)
diff


```

```{r survival regression models on 14 survival, cache=TRUE}
library(dplyr)
chfnoesrd2 <- mutate(chfnoesrd, ProcalGreater2 = PROCALCITONIN.d01 >=2)
data=chfnoesrd2
attach(data)
predict <- cbind(PROCALCITONIN.d01,CR.d01,VentCPT,RRTCPT,ALB.d01,WBC.d01,gender)
## create a surv object
chf.surv <- with(data, Surv(time=as.numeric(Survival),event=two_week))
## fit a surv object based on d01 ProcalGreater than 2
fit <- survfit(chf.surv ~ ProcalGreater2, data=data, conf.int=TRUE)
## plot KM curve with intervals
plot(fit, col=c("green","purple") ,conf.int=TRUE)
## Test for differences in survival objects using survdiff ()
## Test for differences in survival objects using survdiff ()
diff <- with(data, survdiff(Surv(time=Survival,event=two_week)~ProcalGreater2),rho=1)
diff

## Cox PH regression using
predict <- cbind(PROCALCITONIN.d01,CR.d01,VentCPT,RRTCPT,ALB.d01,WBC.d01,gender)
predict <- cbind(PROCALCITONIN.d01)

coxph <- coxph(Surv(time=Survival,event=two_week)~predict, method="breslow")
coxph

## use the parametric models

wiebull <- survreg(Surv(time=Survival,event=two_week)~predict, dist="weibull")
wiebull

exponential <- survreg(Surv(time=Survival,event=two_week)~predict, dist="exponential")
exponential

loglogistic<- survreg(Surv(time=Survival,event=two_week)~predict, dist="loglogistic")
loglogistic

```

