## Exploratory Survival Graphs from d01 Procalcitonin Project and the CHF,ESLD ,GLOBAL, renal failure project

========================================================
```{r}
opts_chunk$set(tidy=TRUE,echo=FALSE,cache=TRUE)

```

```{r loading up the packages}

anonMASTER <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/anonMASTER.csv")

library(ggplot2)
library(caret)
library(dplyr)

```

## Exploratory Graphs

```{r survival lactate, warning=FALSE}
data <- anonMASTER
data <- tbl_df(data)
qplot(LACTATE.d01,Survival,data=data, colour=Survival)
anonMASTER <- mutate(anonMASTER, devakirifle2=(d2max_cr/CR.d01)>=2)
data <- anonMASTER

```

```{r, cache=TRUE, eval=FALSE, echo=FALSE}
qplot(LACTATE.d01,Survival,data=data, colour=Survival, geom=c("point","smooth"), method=lm)

```

```{r,eval=FALSE, echo=FALSE}
qplot(LACTATE.d01,Survival,data=data, colour=Transplant.y, geom=c("point","smooth"), method=lm)

```{r graph, cache=TRUE, eval=FALSE}
qplot(LACTATE.d01,Survival,data=data, colour=ESLD, geom=c("point","smooth"), method=lm)
```

```{r graph ,eval=FALSE, echo=FALSE}
qplot(log(PROCALCITONIN.d01),Survival,data=data,colour=PROCALCITONIN.d01, geom=c("point","smooth"), method=lm)
```

```{r graph procal survival aki, eval=FALSE,cache=TRUE,echo=FALSE}
qplot(log(PROCALCITONIN.d01),Survival,data=data,colour=Transplant.y, geom=c("point","smooth"), method=lm)

```

```{r graph procal survival aki , eval=FALSE,cache=TRUE}
qplot(log(PROCALCITONIN.d01),Survival,data=data,colour=ESLD, geom=c("point","smooth"), method=lm)
```

```{r survival lactate by aki,eval=FALSE ,cache=TRUE, echo=FALSE}
qplot(log(LACTATE.d01),Survival,data=data,colour=aki, geom=c("point","smooth"), method=lm)

qplot(log(PROCALCITONIN.d01),Survival,data=data,colour=aki, geom=c("point","smooth"), method=lm)


```

```{r graph lactate survival by esld,eval=FALSE, cache=TRUE, echo=FALSE}

qplot(log(LACTATE.d01),Survival,data=data,colour=ESLD, geom=c("point","smooth"), method=lm)

```
## ** ESLD AKI  models **

Below we will create a data set esldnowesrd which contains the patients that have a cirrhosis code and do not have a esrd.ckd 5 code.


```{r ESLD Rifle 1}

## define the esld subset and exclude the chronic dialysis patients##
anonmaster4 <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/anonmaster4.csv")
esld <- subset(anonmaster4, ESLD=="ESLD")

esldnonesrd <- subset(esld, ESRD_CKD.5="non ESRD.CKD5")

## glm for predicing the risk of RIFLE stage1  AKI in the encounter in this subset##
g <- glm(devaki~WBC.d01 + log(PROCALCITONIN.d01) + CR.d01 +DM2 + Htn + PLATELETS.d01+LACTATE.d01, data=esldnonesrd, family=binomial(link=logit))

```

## Summary of the GLM for developing renal injury of >= RIFLE stage 1 in hospitalised ESLD patients who do not have prexisting stage 5 ESRD.

```{r}
summary(g)


```


```{r}

## define the esld subset and exclude the chronic dialysis patients##
anonmaster4 <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/anonmaster4.csv")
esld <- subset(anonmaster4, ESLD=="ESLD")

esldnonesrd <- subset(esld, ESRD_CKD.5="non ESRD.CKD5")
## glm for predicing the risk of starting rrt in the encounter in this subset##
rrtbin <- glm(rrtbin ~ WBC.d01 + log(PROCALCITONIN.d01) + CR.d01 +DM2 + Htn + PLATELETS.d01 +LACTATE.d01, data=esldnonesrd, family=binomial(link=logit))

rifle1 <- glm(devaki ~ WBC.d01 + log(PROCALCITONIN.d01) + CR.d01 +DM2 + Htn + PLATELETS.d01 +LACTATE.d01, data=esldnonesrd, family=binomial(link=logit))

```


** Not enough data to look at patients in the rifle2 and rifle 3 categories in ESLD patients. Algorithms dont converge for rifle 2 and rifle 3 patients. The RRT data is shown below.**


```{r rifle2 and rifle 3 aki not enough data }
rifle2 <- glm(devakirifle2 ~ WBC.d01 + log(PROCALCITONIN.d01) + CR.d01 +DM2 + Htn + PLATELETS.d01 +LACTATE.d01, data=esldnonesrd, family=binomial(link=logit))

rifle3  <- glm(devakirifle3 ~ WBC.d01 + log(PROCALCITONIN.d01) + CR.d01 +DM2 + Htn + PLATELETS.d01 +LACTATE.d01, data=esldnonesrd, family=binomial(link=logit))



## GLM for the intiation of RRT in ESLD patients in hospitalised patients. (Not with preexisting ESRD)
summary(rrtbin)

```





## CHF and RRT models


```{r glm chf rrt }
anonmaster4 <- read.csv("~/Desktop/Procalcitonin Day 01 Priject/anonmaster4.csv")
data <- anonmaster4

chf <- subset(data, CHF=="CHF")
chfnoesrd<- subset(chf, ESRD_CKD5=="non ESRD.CKD5" )


glm.chf.rrt <- glm(rrtbin~log(PROCALCITONIN.d01)+ WBC.d01 +CR.d01 + PHtn + ALB.d01+DM2 +min_sodium + min_hb+Htn,data=chfnoesrd, family=binomial)
summary(glm.chf.rrt)

glm.chf.rrt.lact <- glm(rrtbin~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01 +CR.d01 + PHtn + ALB.d01+DM2 +min_sodium + min_hb+Htn,data=chfnoesrd, family=binomial)
summary(glm.chf.rrt.lact)

glm.chf.rrt.lact2 <- glm(rrtbin~LACTATE.d01+CR.d01,data=chfnoesrd, family=binomial)
summary(glm.chf.rrt.lact2)
glm.chf.rrt.lact3 <- glm(rrtbin~log(PROCALCITONIN.d01)+CR.d01,data=chfnoesrd, family=binomial)
summary(glm.chf.rrt.lact3)

qplot( log(PROCALCITONIN.d01),CR.d01-d2max_cr,data=chfnoesrd, colour=rrtbin)

```

## CHF AKI RIFLE Stage I models

```{r CHF AKI RIFLE 1 GLM}


glm.chf.aki <- glm(devaki~log(PROCALCITONIN.d01)+WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=chfnoesrd, family=binomial(link=logit))
summary(glm.chf.aki)

glm.chf.aki.lact <- glm(devaki~log(PROCALCITONIN.d01)+LACTATE.d01+WBC.d01+DM2+PHtn+min_sodium+CR.d01+gender+ALB.d01,data=chfnoesrd, family=binomial(link=logit))

summary(glm.chf.aki.lact)



```

## Stage 1 RIFLE AKI in CHF All Subset Regression

*We will generate all subset regression with the LEAPS package for looking at risk factors for developing AKI in patient with a history of CHF in the dataset. We are using the devaki variable as an outcome (1.5X rise in Cr, over admission day Creatinine)((d2max_cr/cr.d01 > 1.5)*

```{r CHF AKI RIFLE 1 all subsets}
library(MASS)
library(leaps)
attach(chfnoesrd)
leaps <- regsubsets(devaki~log(PROCALCITONIN.d01)+LACTATE.d01+WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=chfnoesrd, nbest=10)

plot(leaps)

```

## Stage 1 RIFLE AKI in CHF Odds ratio table

*We will generate an odds ratio table for looking at risk factors for developing AKI in patient with a history of CHF in the dataset. We are using the devaki variable which essentially corresponds to a rifle stage 1 definition of renal failure (d2max_cr/cr.d01 > 1.5)*

```{r CHF AKI RIFLE 1 odds ratio table}
aki <- glm(formula = devaki ~ log(PROCALCITONIN.d01) + LACTATE.d01 +
WBC.d01 + DM2 + CR.d01 + gender + ALB.d01 + ESLD + PHtn,
family = binomial(link = logit), data = chfnoesrd)
int <- exp(confint(aki))
odds <- exp(coef(aki))
akioddstable <- cbind(odds,int)
akioddstable

```


## CHF AKI RIFLE Stage 2 (d2maxcr/Cr.d01 >2)

*Here we subset the anonMASTER file and define the outcome of RIFLE 2 renal injury. We subset the data for CHF patients and generate and odds ratio table.*


```{r CHF AKI RIFLE 2 GLM ODDS RATIO TABLE (d2maxcr/Cr.d01 >2), warning=FALSE}

anonMASTER <- mutate(anonMASTER, devakirifle2=(d2max_cr/CR.d01)>=2)
data <- anonMASTER
chf <- subset(data, CHF=="CHF")
chfnoesrd<- subset(chf, ESRD_CKD5=="non ESRD.CKD5" )
glm.chf.aki.rifle2 <- glm(devakirifle2~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=chfnoesrd, family=binomial(link=logit))
summary(glm.chf.aki.rifle2)
glmrifle2 <- glm.chf.aki.rifle2 

int <- exp(confint(glm.chf.aki.rifle2))
odds <- exp(coef(glm.chf.aki.rifle2))
akioddstable <- cbind(odds,int)
akioddstable

```

*All subsets regression fo RIFLE2 renal failure in CHF*


```{r CHF RIFLE 2 AKI all subsets, cache=TRUE,warning=FALSE}

library(MASS)
library(leaps)
attach(chfnoesrd)
leaps <- regsubsets(devakirifle2~log(PROCALCITONIN.d01)+LACTATE.d01+WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=chfnoesrd, nbest=10)

plot(leaps)

```

## CHF and RIFLE 3 AKI Models

*We are generating glm models on the outcome of RIFLE 3 Renal failure which includes a Creatinine rise of >3X and or RRT.*



```{r CHF RIFLE 3 AKI GLM, cache=FALSE,warning=TRUE}
library(dplyr)
anonMASTER3 <- mutate(anonMASTER, devakirifle3=(d2max_cr/CR.d01)>=3)
anonmaster3 <- mutate(anonMASTER3,rifle4 = (CR.d01 >=4 & ((d2max_cr-CR.d01)>=0.5)))
anonmaster4 <- mutate(anonmaster3, rifle3 = (devakirifle3=="TRUE" | rrtbin =="TRUE" | rifle4 == "TRUE"))


data <- anonmaster4

chf <- subset(data, CHF=="CHF")

chfnoesrd<- subset(chf, ESRD_CKD5=="non ESRD.CKD5" )
## glm for rifle3
chfrifle3 <- glm(rifle3~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=chfnoesrd, family=binomial(link=logit))

summary(chfrifle3)

##odds ratio table
int <- exp(confint(chfrifle3))
odds <- exp(coef(chfrifle3))
akioddstable <- cbind(odds,int)
akioddstable

```


```{r}

library(glmulti)

chfrifle3 <- glm(rifle3~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+Htn+min_sodium+min_hb,data=chfnoesrd, family=binomial(link=logit), na.action=na.exclude)

multi.chf.model <- glmulti(chfrifle3, # use the model with built as a starting point
                      level = 1,  #  just look at main effects
                      crit="aicc") # use AICc because it works better than AIC for small sample sizes)

summary(multi.chf.model)

```

This is the best model
"rifle3 ~ 1 + log(PROCALCITONIN.d01) + CR.d01 + min_sodium"

Lets run it
```{r, cache=TRUE, echo=TRUE}
library(pROC)
bestchf <- glm(rifle3 ~ 1 + log(PROCALCITONIN.d01) + CR.d01 + min_sodium, data=chfnoesrd,na.action=na.exclude)
m.roc <- roc(chfnoesrd$rifle3, predict(bestchf, backtransform = TRUE))
plot(m.roc)

```

```{r,eval=FALSE}
library(ROCR)
modelpred <- predict(bestchf)
reality <- chfnoesrd$rifle3
pred <- prediction(modelpred$x,reality)
plot(pred)
ed <- as.data.frame(modelpred)

reality <- as.logical(reality)
pred <- prediction(ed,reality)

plot(pred)

```



```

```

*This is an all subsets regression of RIFLE 3 renal failure in CHF patients*

```{r CHF AKI RIFLE 3 all subsets,warning=FALSE}
library(MASS)
library(leaps)
attach(chfnoesrd)
leaps <- regsubsets(rifle3~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=chfnoesrd, family=binomial(link=logit), nbest=10)

plot(leaps)


```

## Global RIFLE 3 Renal Failure

```{r Global  RIFLE 3 Renal Failure,warning=FALSE}

globalnoesrd<- subset(anonmaster4, ESRD_CKD5=="non ESRD.CKD5" )
## the rifle 3 outcome is a composite outcome of patients that had an aki of Cr > 3x and/or initiation or RRT
globalrifle3 <- glm(rifle3~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=globalnoesrd, family=binomial(link=logit))
summary(globalrifle3)




```

## Global RIFLE 2 Renal Failure

```{r Global  RIFLE 2 Renal Failure,warning=FALSE}
leaps <- regsubsets(devakirifle2~log(PROCALCITONIN.d01)+LACTATE.d01+WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=anonmaster4, nbest=10)
plot(leaps,scale="r2")

```

## Ventilator data 
GLM regression for the Vent CPT code, which includes lactate on d01

```{r Vent,cache=TRUE ,warning=FALSE}


glm.chf.vent.lact <- glm(VentCPT~log(PROCALCITONIN.d01)+LACTATE.d01+WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn,data=chfnoesrd, family=binomial(link=logit))
summary(glm.chf.vent.lact)

```



```{r ESLD  AKI RIFLE 1 GLM}


glm.chf.aki <- glm(devaki~log(PROCALCITONIN.d01)+WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn+Htn,data=chfnoesrd, family=binomial(link=logit))
summary(glm.chf.aki)

glm.chf.aki.lact <- glm(devaki~log(PROCALCITONIN.d01)+LACTATE.d01+WBC.d01+DM2+CR.d01+gender+ALB.d01+ESLD+PHtn,data=chfnoesrd, family=binomial(link=logit))

summary(glm.chf.aki.lact)


```

## Multimodel Inference for RIFLE3 GLOBAL
```{r}

```

```{r multimodal inference}
library(glmulti)

globalrifle3 <- glm(rifle3~log(PROCALCITONIN.d01)+LACTATE.d01+ WBC.d01+DM2+CR.d01+gender+ALB.d01+Htn+min_sodium+min_hb,data=globalnoesrd, family=binomial(link=logit), na.action=na.exclude)

multi.global.model <- glmulti(globalrifle3, # use the model with built as a starting point
                      level = 1,  #  just look at main effects
                      crit="aicc") # use AICc because it works better than AIC for small sample sizes)

summary(multi.global.model)
```
Look at the top 10 models, ranked by AICc
```{r}
weightable(multi.global.model)
```

Use the top 5 models

```{r}
library(MuMIn)
library(dplyr)

globalnoesrd2 <- filter(globalnoesrd, CR.d01!=NA)
f<- glm(rifle3 ~ 1 + log(PROCALCITONIN.d01) + CR.d01,data=globalnoesrd, na.action=na.exclude)

```

average the models together
```{r, eval=FALSE}
f.ave <- model.avg(f, f2, f3, f4, f5,na.action=na.exclude)
summary(f.ave)
```



```{r}
library(pROC)

```

Make your reciever-operater curve
```{r GLOBAL AKI RIFLE3 ROC Curve}

m.roc <- roc(globalnoesrd$rifle3, predict(f, backtransform = TRUE))
plot(m.roc)

```